Bounded Model Checking for Embedded Systems \\ (Position Paper)

### 2016-03-18 paper.tex
include new reference

Indeed, many current embedded systems, such as unmanned aerial vehicles (UAVs) and medical monitoring systems~\cite{Cordeiro09}, become interesting solutions only if they can reliably perform their target tasks. For instance, UAVs are a trend on military missions, due to the absence of pilots; however, an incorrect plan execution may also cost human-lives, which is unacceptable. In addition, wrong disease diagnosis or condition-evaluation reports have the potential to compromise patients' health, with serious consequences.

@@

>>>>

Indeed, many current embedded systems, such as unmanned aerial vehicles (UAVs)~\cite{groza2015formal} and medical monitoring systems~\cite{Cordeiro09}, become interesting solutions only if they can reliably perform their target tasks. For instance, UAVs are a trend on military missions, due to the absence of pilots; however, an incorrect plan execution may also cost human-lives, which is unacceptable. In addition, wrong disease diagnosis or condition-evaluation reports have the potential to compromise patients' health, with serious consequences.

@@

\bibitem{groza2015formal}
Groza A., Letia I., Goron A., Zaporojan S.: 
\newblock {\em A formal approach for identifying assurance deficits in unmanned aerial vehicle software}
\newblock In: Progress in Systems Engineering, Springer, pp. 233--239, 2015.
